\subsection{Onboard LED}
This subsection illustrates the use of SPI Communication between the Vaman-ESP32
and the FPGA onboard the Vaman-Pygmy by toggling the LEDs onboard the
Vaman-Pygmy.

\subsubsection{Components}
The components required are listed in \autoref{tab:esp32-fpga-led-components}.
\begin{table}[!ht]
    \centering
    \input{inter-chip/esp32-fpga/led/tables/components.tex}
    \caption{Components Required for Controlling the Onboard LED via SPI.}
    \label{tab:esp32-fpga-led-components}
\end{table}

\subsubsection{Connections}
The connections to be made on the Vaman board are listed in
\autoref{tab:esp32-fpga-led-connections}.
\begin{table}[!ht]
    \centering
    \input{inter-chip/esp32-fpga/led/tables/connections.tex}
    \caption{Connections to Establish SPI between Vaman-ESP32 and Vaman-Pygmy.}
    \label{tab:esp32-fpga-led-connections}
\end{table}

\subsubsection{Building}
\begin{enumerate}
    \item Build the PlatformIO project at
    \begin{lstlisting}
inter-chip/esp32-fpga/led/codes/esp32
    \end{lstlisting}
    \item Flash the project .bin file using USB-UART connected to the 
    Vaman-ESP32, via PlatformIO or ArduinoDroid.
    \item Build the FPGA project .bin file by entering the following commands at
    a terminal window.
    \begin{lstlisting}
# The following variable can be sourced from .shellrc or .venv/bin/activate
export QORC_SDK_PATH=/path/to/pygmy-sdk
cd inter-chip/esp32-fpga/led/codes/fpga
make
    \end{lstlisting}
    \item On building successfully, the .bin file is generated at
    \begin{lstlisting}
inter-chip/esp32-fpga/led/codes/fpga/rtl/AL4S3B_FPGA_Top.bin
    \end{lstlisting}
    \item Flash the .bin file to the Vaman-Pygmy by resetting it to bootloader
    mode and entering the following command at a terminal window,
    \begin{lstlisting}
python3 /path/to/tinyfpga-programmer-gui.py --port /dev/ttyACMxx --mode fpga --appfpga /path/to/AL4S3B_FPGA_Top.bin --reset
    \end{lstlisting}
    where /dev/ttyACMxx is the port at which the Vaman board is available. This
    can be obtained by inspecting the output of the following command (requires
    root/sudo privileges).
    \begin{lstlisting}
dmesg -w
    \end{lstlisting}
\end{enumerate}

\subsubsection{Demonstration}
\begin{enumerate}[resume]
    \item Find the IP address of the Vaman-ESP32 by inspecting the output of the
    serial terminal, or by typing at a terminal window
    \begin{lstlisting}
ifconfig
nmap -sn xx.yy.zz.0/24
    \end{lstlisting}
    where xx.yy.zz represents the first three octets of the IP address of your
    device on the WiFi network interface, found using \texttt{ifconfig}.
    \item Then, go to the following website and interact with the radio buttons
    to toggle the LEDs onboard the Vaman-Pygmy. 
    \begin{lstlisting}
http://<VAMAN-IP>/led
    \end{lstlisting}
\end{enumerate}

\subsubsection{Exercises}
\begin{enumerate}[resume]
    \item Modify the ESP32 code to have three separate radio buttons for each
    onboard LED.
    \item Modify the ESP32 code to blink the LED periodically when the user
    toggles a checkbox on the HTML form.
    \item SPI transactions are a bottleneck in execution. Minimize the number of
    SPI transactions and the amount of data transmitted in each of them.
\end{enumerate}